### 2020-08-29 thesis/thesis.tex
last changes to discussion

However, connectivity research can be hopeful in its ability to move beyond those limitations. Resistance-based models have been validated with genetic data \citep{marrotte_landscape_2014} and occurrence data (telemetry, \cite{gray_landscape_2016}). Although genetic data alone cannot be expected to predict demographic connectivity without information on local demographic rates \citep{lowe_what_2010}, it can provide important information on connectivity when combined with other data sources. Connectivity modelling therefore needs to move toward new, integrative, and data-rich approaches. One example is combining multi-scale resistance surfaces from multiple data types, as \cite{zeller_multi-level_2017} did for pumas (\textit{Puma concolor}) in southern California. The role of novel forms of modelling, such as Agent-Based-Models (ABMs) is another potential direction for connectivity research: they could add realism to resistance based and circuit theory models. In all cases, these approaches are data-intensive and seem to point to a need for more data on animal movements. \\

>>>>

However, connectivity research can be hopeful in its ability to move beyond those limitations. Resistance-based models have been validated with genetic data \citep{marrotte_landscape_2014} and occurrence data (\cite{gray_landscape_2016}) and movement data \citep{lapoint_animal_2013}. Although genetic data alone cannot be expected to predict demographic connectivity without information on local demographic rates \citep{lowe_what_2010}, it can provide important information on connectivity when combined with other data sources. Connectivity modelling therefore needs to move toward new, integrative, and data-rich approaches. One example is combining multi-scale resistance surfaces from multiple data types, as \cite{zeller_multi-level_2017} did for pumas (\textit{Puma concolor}) in southern California. The role of novel forms of modelling, such as Individual-BasedModels (IBMs, a form of Agents-Based Models) is another potential direction for connectivity research: they can add realism to resistance based and circuit theory models and bring attention to mechanisms overlooked by those models, like mortality \citep{day_individual-based_2020}. In all cases, these approaches are data-intensive and seem to point to a need for more data on animal movements. \\
